Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2020-01-14 ms.tex
showing unaligned versus mostly aligned time series

\begin{figure*}
\gridline{\fig{comparison_spec_otis_flat_vs_no_flat.pdf}{0.55\textwidth}{}}
\caption{The position variations along the dispersion direction cause large fluctuations in the time series.
}\label{fig:otisLWflatVsNoFlat}
\end{figure*}

@@

\begin{figure*}
\gridline{\fig{wavebin_tser_o9LEDwFlat_NRCN83-256-O9LW.pdf}{0.55\textwidth}{}}
\caption{Flat fielding has a pronounced effect of reducing the crosshatch pattern in the spectrum.
The offset between the spectra are likely due to the non-linearity corrections applied to the flat fielded data.
}\label{fig:otisWavebinTSeries}
\end{figure*}

>>>>

\begin{figure*}
\gridline{\fig{comparison_spec_otis_flat_vs_no_flat.pdf}{0.55\textwidth}{}}
\caption{Flat fielding has a pronounced effect of reducing the crosshatch pattern in the spectrum.
The crosshatch pattern is also 
The offset between the spectra are likely due to the non-linearity corrections applied to the flat fielded data.
}\label{fig:otisLWflatVsNoFlat}
\end{figure*}

@@

\begin{figure*}
\gridline{\fig{wavebin_tser_o9LEDwFlat_NRCN83-256-O9LW.pdf}{0.49\textwidth}{Time Series without Alignment}
\fig{wavebin_tser_o9LEDwf322w2Flat_NRCN83-256-O9LW_aligned.pdf}{0.49\textwidth}{Time Series with Alignment}}
\caption{The position variations along the dispersion direction cause large fluctuations in the time series.
These are dramatically reduced when cross-correlating and finding the peak to adjust for wavelength shifts
}\label{fig:otisWavebinTSeries}
\end{figure*}
